---
title: "Astrios QC tools"
author: "Created by: Joshua L Schipper"
date: "September 4, 2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning = FALSE, message = FALSE)

# packages --------------------------------------------------------------------
library(shiny)

```

```{r}

shinyApp(
  ui <- fluidPage( # setting up user interface
    
    # file upload manager
    fileInput("files", label = h3("Select QC files"),
              accept = c(
                "text/csv",
                "text/comma-separated-values,text/plain",
                ".csv"),
              multiple = TRUE),
    
    uiOutput("buttons")
    
  
  ),
  
  server <- function(input, output, session) { # actually doing the stuff
    
    # Only show buttons for reports after file(s) have been uploaded
    output$buttons <- renderUI ({ 
      if(is.null(input$files)){return()} #don't do anything if no files
      list( #show these action buttons if files are uploaded
        downloadButton("LJreport", "Generate LJ Plots"),
        downloadButton("QCreport", "Generate QC report")
        )
    })
    
    # Generate QC report on button click
    output$QCreport <- downloadHandler(
      filename = function() { paste("QC_report_", format(Sys.time(), "%Y-%m-%d_%H.%M.%S"), ".html", sep="") },
      content = function(file) {
        tempReport <- file.path(tempdir(), "QCreport.Rmd")
        file.copy("QCreport.Rmd", tempReport, overwrite = TRUE)
        params <- list(f=input$files)
        rmarkdown::render(tempReport, output_file = file,
                          params = params,
                          envir = new.env(parent = globalenv()) )
      }
    )
    
    # Generate LJ plots for CV on button click
    output$LJreport <- downloadHandler(
      filename = function() { paste("LJ_report_", format(Sys.time(), "%Y-%m-%d_%H.%M.%S"), ".html", sep="") },
      content = function(file) {
        tempReport <- file.path(tempdir(), "LJreport.Rmd")
        file.copy("LJreport.Rmd", tempReport, overwrite = TRUE)
        params <- list(f=input$files)
        rmarkdown::render(tempReport, output_file = file,
                          params = params,
                          envir = new.env(parent = globalenv()) )
      }
    )   
    

  }
)

```
 LJ Plot Report Notes:  
 -This can take a few seconds to run, especially if there are a lot of files.
 -This will work for different laser/detector configurations, although it is not recommended to use with a range of QC files that include large numbers of different configurations.  
 -If multiple QC files exist for a given day, only the last one will be used.  
 -Horizontal line represents most current pass threshold.  
   
 QC report Notes:  
 -If more than one file is selected, the report will only be generated for the latest one.  
 -PMT voltage, and CV values that did not pass are colored in red.  
 